working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect

### 2018-12-08 Manuscript_draft/Manuscript_draft.Rmd
Some edits

Recent studies have advanced in the ecological understanding of heterospecific pollen effect @morales2008 @ashman2013 @arceo2016. A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008. Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 0 and 20 percent of the total pollen load @bartomeus2008 @montgomery2012 @ashman2013 @fang2013, being the generalist species the ones that receive greater loads of heterospecific pollen @fang2013. Surprisingly, this low ranges of heterospecific pollen have been shown to decrease fitness greatly @thomson1982. Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient. @ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect, where different traits such as compatibility system and pollen size among others seems to be crucial to understand foreing pollen effect. Moreover, in @tong2016 an assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the full length of the style on short styled species but not viceversa. Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level. Interestingly, to comprehend how these traits interact is also crucial to look at the phylogenetic relatedness of the species. There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 but few works focused on heterospecific pollen of far related species. Although the effect of close related species is predicted to be greater @ashman2013 the presence of pollen of non related species on multiple species @arceo2016 and the higher chances to coexist with a species that has less niche overlap (Ref) make foreign pollen from far related species also an important subject of study in order to understand the importance of heterospecific pollen in natural systems. Notwithstanding, the effect of heterospecific pollen of far and close related species at community level remains to be explored beyond single pairwise interactions.

@@

Interestingly, incompatibility system seems to play an important role in foreign pollen effect where species that are self incompatible would have stronger barriers towards heterospecific pollen than self compatible species @ashman2013. The type of incompatibility, sporophytic or gametophytic is related with the place of pollen recognition where the former take place at the sitgma level and the latter occurs within the style, this last late acting pollen recognition mechanism is associated with greater negative effect @barrett1999. Remarkably, there is a great variability in mating systems across populations @whitehead2018 and therefore predict an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018). Moreover, other traits such as number of pollen grains per flower and number of ovules have been tradittionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF). Selfer species would have a reduction of herkogamy (REF), less pollen production per ovule (REF) and therefore less likely to contribute in exporting pollen in the community. Other morphological traits, like stigma size can be determinant for the total pollen quatity that a stigma can receive and therefore related to do that pollen size would also play an important role. Example with pollen here.

@@

Brown and Mitchell 2001 could be a good paper to explain why we pick seed set as a proxy and not fruit set. We cannot see changes on it, losing information with it.

@@

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10). Seed set was the proxy of effect (see Brown and Mitchell 2001, for differences in effect between seed set and fruit set) and "pollen tubes". Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested (N=10). Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Had-pollination was realized with 3-4 gentle touches on the surface of the stigma. The mixes of pollen were performed on an eppendorf based on the pollen counts maded with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species).

**Evolutive distance**

Two types of evolutive distances were calculated with MEGA7 for two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL)

**Traits**

The traits measured for each species were pollen per anther, number of ovules, stigma width and length and stigmatic area, style width and length, ovary width and length. Moreover stigma type was tested. Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer. Previously anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds. Ovule number was counted with the help of an stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers. The different morphometrical traits were measured with XXXX. Levels of self incompatibility were estimated by dividing the the fruit set of hand self pollination by hand cross pollination

```{r model, echo = FALSE, eval = FALSE}
model <- lm(y ~ x)
```

@@

>>>>

Recent studies have advanced in the ecological understanding of heterospecific pollen effect @morales2008 @ashman2013 @arceo2016. A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008. Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 0 and 20 percent of the total pollen load @bartomeus2008 @montgomery2012 @ashman2013 @fang2013, being the generalist species the ones that receive greater loads of heterospecific pollen @fang2013. Surprisingly, this low ranges of heterospecific pollen have been shown to decrease fitness greatly @thomson1982. Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient. @ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect, where different traits such as compatibility system and pollen size among others seems to be crucial to understand foreing pollen effect. Moreover, in @tong2016 an assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the full length of the style on short styled species but not viceversa. Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level. Interestingly, to comprehend how these traits interact is also crucial to look at the phylogenetic relatedness of the species. There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 but few works focused on heterospecific pollen of far related species @thomson1982 @galen1989 @neiland1999 which also show a noteworthy fitness decrease. Although the effect of close related species is predicted to be greater @ashman2013 the presence of pollen of non related species on multiple species @arceo2016 and the higher chances to coexist with a species that has less niche overlap (Ref) make foreign pollen from far related species also an important subject of study in order to understand the importance of heterospecific pollen in natural systems. Notwithstanding, the effect of heterospecific pollen of far and close related species at community level remains to be explored beyond single pairwise interactions.

@@

Interestingly, incompatibility system seems to play an important role in foreign pollen effect where species that are self incompatible would have stronger barriers towards heterospecific pollen than self compatible species @ashman2013. The type of incompatibility, sporophytic or gametophytic is related with the place of pollen recognition where the former take place at the sitgma level and the latter occurs within the style, this last late acting pollen recognition mechanism is associated with greater negative effect @barrett1988. Remarkably, there is a great variability in mating systems across populations @whitehead2018 and therefore predict an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018). Moreover, other traits such as number of pollen grains per flower and number of ovules have been tradittionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF). Selfer species would have a reduction of herkogamy (REF), less pollen production per ovule (REF) and therefore less likely to contribute in exporting pollen in the community. Other morphological traits, like stigma size can be determinant for the total pollen quatity that a stigma can receive and therefore related to do that pollen size would also play an important role. Example with pollen here.

@@

**Table 1**
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
Family <- c(rep("Brassicaceae",4), rep("Convolvulaceae", 2), rep("Solanaceae",4))

Genus <- c("Brassica", "Brassica", "Eruca", "Sinapis", "Ipomoea", "Ipomoea", "Capsicum", "Petunia", "Solanum", "Solanum")

Species <- c("Brassica rapa", "Brassica oleracea", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")

table<- data.frame(Family, Genus, Species)
kable(table, format="markdown")
```

@@

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10). Therefore, 180 different combinations were perform with N=10. Seed set was the proxy of effect for all our teratments. Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested (N=10). Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Had-pollination was realized with 3-4 gentle touches on the surface of the stigma. The mixes of pollen were performed on an eppendorf based on the pollen counts maded with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species).

**Traits and evolutive distance**

The traits measured for each species were pollen per anther, number of ovules, stigma width and length and stigmatic area, style width and length, ovary width and length. Moreover stigma type was tested. Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer. Previously anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds. Ovule number was counted with the help of an stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers. The different morphometrical traits were measured with XXXX. Levels of self incompatibility were estimated by dividing the the fruit set of hand self pollination by hand cross pollination. Moreover, two types of evolutive distances were calculated with MEGA7 for two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL)

**Analysis**

@@

Heterospecific pollen produced fitness for xxx cases.

### 2018-12-08 Manuscript_draft/Manuscript_draft.tex
Some edits

\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

Recent studies have advanced in the ecological understanding of
heterospecific pollen effect Morales and Traveset (2008) Ashman and
Arceo-Gómez (2013) Arceo-Gómez and Ashman (2016). A general overview of
foreign pollen arrival is that it can play an important role on species
fitness but seems to be context dependent and not always produce a
decrease in fitness Morales and Traveset (2008). Part of this
unpredictability is due to the enormous variability of foreing pollen
transferred in nature, where levels between 0 and 75 percent are seen,
but most commonly values ranges between 0 and 20 percent of the total
pollen load Bartomeus et al. (2008) Montgomery and Rathcke (2012) Ashman
and Arceo-Gómez (2013) Fang and Huang (2013), being the generalist
species the ones that receive greater loads of heterospecific pollen
Fang and Huang (2013). Surprisingly, this low ranges of heterospecific
pollen have been shown to decrease fitness greatly Thomson et al.
(1982). Although heterospecific pollen quantity is fundamental to
understand the outcome of the interaction so is the different traits of
both pollen donor and recipient. Ashman and Arceo-Gómez (2013)
postulated the first predictive framework for traits of heterospecific
pollen effect, where different traits such as compatibility system and
pollen size among others seems to be crucial to understand foreing
pollen effect. Moreover, in Tong and Huang (2016) an assymetric effect
was shown in a crossing experiment between 6 species of the genus
\emph{Pedicularis} where the pollen of long styled species was able to
grow the full length of the style on short styled species but not
viceversa. Despite these recent caveats, we still lack empirical
evidence to affirm what are the main traits that drive heterospecific
pollen effect for both pollen donor and recipient at seed production
level. Interestingly, to comprehend how these traits interact is also
crucial to look at the phylogenetic relatedness of the species. There is
a considerable amount of literature of crosses between close related
species Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and
Huang (2016) but few works focused on heterospecific pollen of far
related species. Although the effect of close related species is
predicted to be greater Ashman and Arceo-Gómez (2013) the presence of
pollen of non related species on multiple species Arceo-Gómez and Ashman
(2016) and the higher chances to coexist with a species that has less
niche overlap (Ref) make foreign pollen from far related species also an
important subject of study in order to understand the importance of
heterospecific pollen in natural systems. Notwithstanding, the effect of
heterospecific pollen of far and close related species at community
level remains to be explored beyond single pairwise interactions.

@@

Interestingly, incompatibility system seems to play an important role in
foreign pollen effect where species that are self incompatible would
have stronger barriers towards heterospecific pollen than self
compatible species Ashman and Arceo-Gómez (2013). The type of
incompatibility, sporophytic or gametophytic is related with the place
of pollen recognition where the former take place at the sitgma level
and the latter occurs within the style, this last late acting pollen
recognition mechanism is associated with greater negative effect
({\textbf{???}}). Remarkably, there is a great variability in mating
systems across populations Whitehead et al. (2018) and therefore predict
an effect of foreign pollen is a bit obscured by the variability within
species, however species that are strong selfers or strong outcrossers
have less variablity in mating systems and predictions of effect could
be more realistic (see figure 1 from Whitehead et al. (2018)). Moreover,
other traits such as number of pollen grains per flower and number of
ovules have been tradittionally associated with the type of
incompatibility system where species with higher pollen ovule ratios are
predicted to be xenogamous and species with low pollen ovule ratios
autogamous (REF). Selfer species would have a reduction of herkogamy
(REF), less pollen production per ovule (REF) and therefore less likely
to contribute in exporting pollen in the community. Other morphological
traits, like stigma size can be determinant for the total pollen quatity
that a stigma can receive and therefore related to do that pollen size
would also play an important role. Example with pollen here.

@@

Brown and Mitchell 2001 could be a good paper to explain why we pick
seed set as a proxy and not fruit set. We cannot see changes on it,
losing information with it.

@@

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen (N=10). Seed set was the proxy of effect
(see Brown and Mitchell 2001, for differences in effect between seed set
and fruit set) and ``pollen tubes''. Moreover, hand cross pollination,
hand self pollination, apomixis (bagged emasculated flowers) and natural
selfing were tested (N=10). Flowers were emasculated the day prior
anthesis and hand pollinated next day with a toothpick. Had-pollination
was realized with 3-4 gentle touches on the surface of the stigma. The
mixes of pollen were performed on an eppendorf based on the pollen
counts maded with Neubaeur chamber (each anther was counted 4 times for
20 different anthers per species).

\textbf{Evolutive distance}

Two types of evolutive distances were calculated with MEGA7 for two
kinds of markers: 1) Internal transcribed spacer (ITS) and 2)
ribulose-bisphosphate carboxylase (RBCL)

\textbf{Traits}

The traits measured for each species were pollen per anther, number of
ovules, stigma width and length and stigmatic area, style width and
length, ovary width and length. Moreover stigma type was tested. Pollen
was counted for 20 anthers of each species with 4 replicates per sample
with an hemocytometer. Previously anthers were squashed on a known
solution with the pippete tip and homogeneize with a vortex for 30
seconds. Ovule number was counted with the help of an stereomicroscope
and a small grid over a petri dish from 15 randomly selected flowers.
The different morphometrical traits were measured with XXXX. Levels of
self incompatibility were estimated by dividing the the fruit set of
hand self pollination by hand cross pollination

@@

@@

@@

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

@@

Recent studies have advanced in the ecological understanding of
heterospecific pollen effect Morales and Traveset (2008) Ashman and
Arceo-Gómez (2013) Arceo-Gómez and Ashman (2016). A general overview of
foreign pollen arrival is that it can play an important role on species
fitness but seems to be context dependent and not always produce a
decrease in fitness Morales and Traveset (2008). Part of this
unpredictability is due to the enormous variability of foreing pollen
transferred in nature, where levels between 0 and 75 percent are seen,
but most commonly values ranges between 0 and 20 percent of the total
pollen load Bartomeus et al. (2008) Montgomery and Rathcke (2012) Ashman
and Arceo-Gómez (2013) Fang and Huang (2013), being the generalist
species the ones that receive greater loads of heterospecific pollen
Fang and Huang (2013). Surprisingly, this low ranges of heterospecific
pollen have been shown to decrease fitness greatly Thomson et al.
(1982). Although heterospecific pollen quantity is fundamental to
understand the outcome of the interaction so is the different traits of
both pollen donor and recipient. Ashman and Arceo-Gómez (2013)
postulated the first predictive framework for traits of heterospecific
pollen effect, where different traits such as compatibility system and
pollen size among others seems to be crucial to understand foreing
pollen effect. Moreover, in Tong and Huang (2016) an assymetric effect
was shown in a crossing experiment between 6 species of the genus
\emph{Pedicularis} where the pollen of long styled species was able to
grow the full length of the style on short styled species but not
viceversa. Despite these recent caveats, we still lack empirical
evidence to affirm what are the main traits that drive heterospecific
pollen effect for both pollen donor and recipient at seed production
level. Interestingly, to comprehend how these traits interact is also
crucial to look at the phylogenetic relatedness of the species. There is
a considerable amount of literature of crosses between close related
species Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and
Huang (2016) but few works focused on heterospecific pollen of far
related species Thomson et al. (1982) Galen and Gregory (1989) Neiland
and Wilcock (1999) which also show a noteworthy fitness decrease.
Although the effect of close related species is predicted to be greater
Ashman and Arceo-Gómez (2013) the presence of pollen of non related
species on multiple species Arceo-Gómez and Ashman (2016) and the higher
chances to coexist with a species that has less niche overlap (Ref) make
foreign pollen from far related species also an important subject of
study in order to understand the importance of heterospecific pollen in
natural systems. Notwithstanding, the effect of heterospecific pollen of
far and close related species at community level remains to be explored
beyond single pairwise interactions.

@@

Interestingly, incompatibility system seems to play an important role in
foreign pollen effect where species that are self incompatible would
have stronger barriers towards heterospecific pollen than self
compatible species Ashman and Arceo-Gómez (2013). The type of
incompatibility, sporophytic or gametophytic is related with the place
of pollen recognition where the former take place at the sitgma level
and the latter occurs within the style, this last late acting pollen
recognition mechanism is associated with greater negative effect Barrett
(1988). Remarkably, there is a great variability in mating systems
across populations Whitehead et al. (2018) and therefore predict an
effect of foreign pollen is a bit obscured by the variability within
species, however species that are strong selfers or strong outcrossers
have less variablity in mating systems and predictions of effect could
be more realistic (see figure 1 from Whitehead et al. (2018)). Moreover,
other traits such as number of pollen grains per flower and number of
ovules have been tradittionally associated with the type of
incompatibility system where species with higher pollen ovule ratios are
predicted to be xenogamous and species with low pollen ovule ratios
autogamous (REF). Selfer species would have a reduction of herkogamy
(REF), less pollen production per ovule (REF) and therefore less likely
to contribute in exporting pollen in the community. Other morphological
traits, like stigma size can be determinant for the total pollen quatity
that a stigma can receive and therefore related to do that pollen size
would also play an important role. Example with pollen here.

@@

\textbf{Table 1}

\begin{longtable}[]{@{}lll@{}}
\toprule
Family & Genus & Species\tabularnewline
\midrule
\endhead
Brassicaceae & Brassica & Brassica rapa\tabularnewline
Brassicaceae & Brassica & Brassica oleracea\tabularnewline
Brassicaceae & Eruca & Eruca versicaria\tabularnewline
Brassicaceae & Sinapis & Sinapis alba\tabularnewline
Convolvulaceae & Ipomoea & Ipomoea aquatica\tabularnewline
Convolvulaceae & Ipomoea & Ipomoea purpurea\tabularnewline
Solanaceae & Capsicum & Capsicum annuum\tabularnewline
Solanaceae & Petunia & Petunia integrifolia\tabularnewline
Solanaceae & Solanum & Solanum lycopersicum\tabularnewline
Solanaceae & Solanum & Solanum melongena\tabularnewline
\bottomrule
\end{longtable}

@@

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen (N=10). Therefore, 180 different
combinations were perform with N=10. Seed set was the proxy of effect
for all our teratments. Moreover, hand cross pollination, hand self
pollination, apomixis (bagged emasculated flowers) and natural selfing
were tested (N=10). Flowers were emasculated the day prior anthesis and
hand pollinated next day with a toothpick. Had-pollination was realized
with 3-4 gentle touches on the surface of the stigma. The mixes of
pollen were performed on an eppendorf based on the pollen counts maded
with Neubaeur chamber (each anther was counted 4 times for 20 different
anthers per species).

\textbf{Traits and evolutive distance}

The traits measured for each species were pollen per anther, number of
ovules, stigma width and length and stigmatic area, style width and
length, ovary width and length. Moreover stigma type was tested. Pollen
was counted for 20 anthers of each species with 4 replicates per sample
with an hemocytometer. Previously anthers were squashed on a known
solution with the pippete tip and homogeneize with a vortex for 30
seconds. Ovule number was counted with the help of an stereomicroscope
and a small grid over a petri dish from 15 randomly selected flowers.
The different morphometrical traits were measured with XXXX. Levels of
self incompatibility were estimated by dividing the the fruit set of
hand self pollination by hand cross pollination. Moreover, two types of
evolutive distances were calculated with MEGA7 for two kinds of markers:
1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate
carboxylase (RBCL)

\textbf{Analysis}

@@

\hypertarget{ref-barrett1988}{}
Barrett, S. C. 1988. The evolution, maintenance, and loss of
self-incompatibility systems. Plant reproductive ecology: patterns and
strategies:98--124.

@@

\hypertarget{ref-galen1989}{}
Galen, C., and T. Gregory. 1989. Interspecific pollen transfer as a
mechanism of competition: Consequences of foreign pollen contamination
for seed set in the alpine wildflower, polemonium viscosum. Oecologia
81:120--123.

@@

\hypertarget{ref-neiland1999}{}
Neiland, M., and C. Wilcock. 1999. The presence of heterospecific pollen
on stigmas of nectariferous and nectarless orchids and its consequences
for their reproductive success. Protoplasma 208:65--75.
